PyQBench: a Python library for benchmarking gate-based quantum computers

### 2023-08-26 reviews/softwarex/reviews_1/response/response.tex

\newenvironment{response}{\vspace{1em}\noindent\textbf{Response}}{\vspace{1em}}

\begin{document}
We would like to thank the reviewers for their comments. Below we provide
a response to their specific remarks.

\section{Reviewer 1}

\begin{enumerate}
  \item[] In my opinion, the weakest part of the paper is the lack of a more detailed analysis of the pros and cons of the suggested benchmarking scheme and its thorough comparison with other existing NISQ benchmarking schemes. Thus, I recommend a minor revision where I would ask the authors to better describe advantages and disadvantages of the suggested NISQ benchmarking scheme with respect to other existing NISQ benchmarking techniques. Although the focus of the paper is the PyQBench software, I find it important for the reader to have a clear understanding where and how the underlying NISQ benchmarking technique and corresponding software are superior to other available techniques and software.

  \begin{response}
    We improved the manuscript, which now includes a short section explaining the pros and cons of our method in the context of other existing benchmarking methods. Due to the length limitations in the journal, we do not think this section can become any longer, but we are open to further improvement suggestions if the reviewer finds the current analysis lacking.
  \end{response}
  \item The cross-entropy benchmarking technique used in the validation of the Sycamore-53 QPU in
    quantum supremacy experiments (\url{https://www.nature.com/articles/s41586-019-1666-5}) should also
    be mentioned in the Introduction (\url{https://www.nature.com/articles/s41567-018-0124-x}).

### 2023-08-26 reviews/softwarex/reviews_1/response/response.tex

\newenvironment{response}{\vspace{1em}\noindent\textbf{Response}}{\vspace{1em}}

\begin{document}
We would like to thank the reviewers for their comments. Below we provide
a response to their specific remarks.

\section{Reviewer 1}

\begin{enumerate}
  \item  In my opinion, the weakest part of the paper is the lack of a more
    detailed analysis of the pros and cons of the suggested benchmarking scheme
    and its thorough comparison with other existing NISQ benchmarking schemes.
    Thus, I recommend a minor revision where I would ask the authors to better
    describe advantages and disadvantages of the suggested NISQ benchmarking
    scheme with respect to other existing NISQ benchmarking techniques.
    Although the focus of the paper is the PyQBench software, I find it
    important for the reader to have a clear understanding where and how the
    underlying NISQ benchmarking technique and corresponding software are
    superior to other available techniques and software.

### 2023-08-26 reviews/softwarex/reviews_1/response/response.tex

\begin{document}
We would like to thank the reviewers for their comments. Below we provide
a response to their specific remarks.

\section{Reviewer 1}

\begin{enumerate}
  \item  In my opinion, the weakest part of the paper is the lack of a more
    detailed analysis of the pros and cons of the suggested benchmarking scheme
    and its thorough comparison with other existing NISQ benchmarking schemes.
    Thus, I recommend a minor revision where I would ask the authors to better
    describe advantages and disadvantages of the suggested NISQ benchmarking
    scheme with respect to other existing NISQ benchmarking techniques.
    Although the focus of the paper is the PyQBench software, I find it
    important for the reader to have a clear understanding where and how the
    underlying NISQ benchmarking technique and corresponding software are
    superior to other available techniques and software.

    \begin{response}
      We improved the manuscript, which now includes a short section explaining
      the pros and cons of our method in the context of other existing
      benchmarking methods. Due to the length limitations in the journal, we do
      not think this section can become any longer, but we are open to further
      improvement suggestions if the reviewer finds the current analysis
      lacking.
    \end{response}
  \item When discussing the existing quantum computing frameworks, the
    Introduction should also mention the XACC framework which is known for its
    cross-architectural as well as cross-language portability
    (https://iopscience.iop.org/article/10.1088/2058-9565/ab6bf6).
    Additionally, the recent CUDA-Quantum framework backed by NVIDIA
    (https://github.com/NVIDIA/cuda-quantum) is worth mentioning as well.
    \begin{response}
      Both XACC and CUDA Quantum have now been mentioned in the manuscript.
    \end{response}
  \item The cross-entropy benchmarking technique used in the validation of the
    Sycamore-53 QPU in quantum supremacy experiments
    (\url{https://www.nature.com/articles/s41586-019-1666-5}) should also be
    mentioned in the Introduction
    (\url{https://www.nature.com/articles/s41567-018-0124-x}).

### 2023-08-27 txt/manuscript_short.tex
Add references to XACC and CUDA Quantum
Respond to reviewers and improve manuscript (#15)
* Add references to XACC and CUDA Quantum

* Add response about XACC and CUDA Quantum to response file

* Add figure with architecture overview.

Noisy Intermediate-Scale Quantum (NISQ)~\cite{preskill} devices are storming the market, with a wide
selection of devices based on different architectures and accompanying software solutions. Among
hardware providers offering public access to their gate--based devices, one could mention Rigetti
\cite{rigetti}, IBM \cite{ibmq}, Oxford Quantum Group \cite{oxforf}, IonQ \cite{ionq} or Xanadu
\cite{xanadu}. Other vendors offer devices operating in different paradigms. Notably, one could
mention D-Wave \cite{dwave} and their quantum annealers, or QuEra devices \cite{quera} based on
neural atoms. Most vendors provide their own software stack and application programming interface
for accessing their devices. To name a few, Rigetti's computers are available through their Forest
SDK \cite{sdk} and PyQuil library \cite{pyquil} and IBM Q \cite{ibmq} computers can be accessed
through Qiskit \cite{qiskit} or IBM Quantum Experience web interface \cite{ibmqplatform}. Some cloud
services, like Amazon Braket \cite{amazon}, offer access to several quantum devices under a unified
API. On top of that, several libraries and frameworks can integrate with multiple hardware vendors.
Examples of such frameworks include IBM Q's Qiskit or Zapata Computing's Orquestra \cite{zapata}.

@@

\subsubsection{Overview of the software structure}
As already described, PyQBench can be used both as a library and a CLI. Both functionalities are
implemented as a part of \texttt{qbench} Python package. The exposed CLI tool is also named
\texttt{qbench}. For brevity, we do not discuss the exact structure of the package here, and instead
refer an interested reader to the source code available at GitHub \cite{pyqbenchgithub} or at the
reference manual \cite{pyqbenchdocs}.

>>>>

Noisy Intermediate-Scale Quantum (NISQ)~\cite{preskill} devices are storming the market, with a wide
selection of devices based on different architectures and accompanying software solutions. Among
hardware providers offering public access to their gate--based devices, one could mention Rigetti
\cite{rigetti}, IBM \cite{ibmq}, Oxford Quantum Group \cite{oxforf}, IonQ \cite{ionq} or Xanadu
\cite{xanadu}. Other vendors offer devices operating in different paradigms. Notably, one could
mention D-Wave \cite{dwave} and their quantum annealers, or QuEra devices \cite{quera} based on
neural atoms. Most vendors provide their own software stack and application programming interface
for accessing their devices. To name a few, Rigetti's computers are available through their Forest
SDK \cite{sdk} and PyQuil library \cite{pyquil} and IBM Q \cite{ibmq} computers can be accessed
through Qiskit \cite{qiskit} or IBM Quantum Experience web interface \cite{ibmqplatform}. Some cloud
services, like Amazon Braket \cite{amazon}, offer access to several quantum devices under a unified
API. On top of that, several libraries and frameworks can integrate with multiple hardware vendors.
Examples of such frameworks include IBM Q's Qiskit, Zapata Computing's Orquestra \cite{zapata}, XACC \cite{xacc} and NVIDIA's CUDA Quantum \cite{cudaquantum}.

@@

\subsubsection{Overview of the software structure}
As already described, PyQBench can be used both as a library and a CLI. Both functionalities are
implemented as a part of \texttt{qbench} Python package. The exposed CLI tool is also named
\texttt{qbench}. For brevity, we do not discuss the exact structure of the package here, and instead limit ourselves to summarizing the architecture on the diagram in Fig. \ref{fig:architecture}. For further details, we refer an interested reader to the source code available at GitHub \cite{pyqbenchgithub} or at the
reference manual \cite{pyqbenchdocs}.

\begin{figure}
  \includegraphics[width=\textwidth]{pics/architecture.pdf}
  \caption{Overview of PyQBench's architecture.}
  \label{fig:architecture}
\end{figure}
